---
title: "statistics project"
author: "Nguyen Ngoc Duy"
output:
  pdf_document: default
  html_document: default
---
## Part 1: Simulation Exercise Instructions
### 1.1 Simulations:
```{r}
#install.packages("tinytex")
library(tidyverse)
```

```{r}
### As a motivating example, compare the distribution of 1000 random uniforms
#hist(runif(1000))
#and the distribution of 1000 averages of 40 random uniforms
#mns = NULL
#for (i in 1 : 1000) mns = c(mns, mean(runif(40)))
#hist(mns)
```

Distribution of a large collection of random exponentials

```{r}
lambda <- 0.2
n <- 1000
random_exponentials <- runif(rexp(n,lambda))
hist(random_exponentials)
```

Distribution of a large collection of averages of 40 exponentials.
```{r}
mns = NULL
n=40
for (i in 1 : 1000) mns = c(mns, mean(runif(rexp(n,lambda) )))
average_exponentials <- mns
hist(average_exponentials)
```

```{r}
data_combine <- cbind(random_exponentials,average_exponentials)
```

```{r}
library(reshape2)
data_combine_melt <- melt(data_combine)
head(data_combine_melt)
```

### 1.2 Show the sample mean and compare it to the theoretical mean of the distribution.
```{r}
population_mean <- mean(random_exponentials)
sample_mean <- mean(average_exponentials)
sample_mean
population_mean
```
Sample_mean and population_mean is nearly the same
```{r}
data_combine_melt %>% 
  ggplot(aes(x=Var2,y=value)) +
  geom_boxplot()
```


### 1.3. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
```{r}
population_var <- var(random_exponentials)
sample_var <- var(average_exponentials)
sample_var
population_var
```
Large different between sample and population variance
### 1.4. Show that the distribution is approximately normal.
```{r}
qqnorm(average_exponentials)
qqline(average_exponentials, col = 2)
```

```{r}
# Test normal distribution
shapiro.test(average_exponentials)
```
From the output, the p-value > 0.05 implying that the distribution of the data are not significantly different from normal distribution. In other words, we can assume the normality.

