---
title: "Data_science"
output: html_document
---
# R Programming Week 2
# Programming Assignment 1 INSTRUCTIONS: Air Pollution

```{r}
path <- "specdata"
```

```{r}
mydir = "specdata"
myfiles = list.files(path=mydir, pattern="*.csv", full.names=TRUE)
myfiles
```
```{r}
myfiles[1:10]
```

```{r}
library(plyr)
dat_csv = ldply(myfiles, read_csv)
dat_csv
```
```{r}
dat_csv %>% select(sulfate) %>% colMeans( na.rm = TRUE)
```

```{r}
library(readr)
X001 <- read_csv("specdata/001.csv")
X001
```
```{r}
count(X001,na.rm=T)
dim(X001)[1]
```


```{r}
cbind(path,3,1)
```

Part 1
Write a function named 'pollutantmean' that calculates the mean of a pollutant (sulfate or nitrate) across a specified list of monitors. The function 'pollutantmean' takes three arguments: 'directory', 'pollutant', and 'id'. Given a vector monitor ID numbers, 'pollutantmean' reads that monitors' particulate matter data from the directory specified in the 'directory' argument and returns the mean of the pollutant across all of the monitors, ignoring any missing values coded as NA. A prototype of the function is as follows
```{r}
library(plyr)
library(tidyverse)
pollutantmean <- function(directory, pollutant, id = 1:332){
  
  myfiles = list.files(path=directory, pattern="*.csv", full.names=TRUE)[id]
  dat_csv = plyr::ldply(myfiles, read_csv) # read and combine
  dat_csv%>% select(pollutant) %>% colMeans( na.rm = TRUE)
}
```


```{r}
pollutantmean("specdata", "sulfate", 1:10)
```

```{r}
pollutantmean("specdata", "nitrate", 70:72)
```

```{r}
# Best method
pollutantmean <- function(directory, pollutant, id = 1:332) {
     ## obtaining the required files by storing them into mydata variable
     mydata <- list.files(path = directory,pattern="*.csv", full.names=TRUE)[id]
     ## reading the .csv files of mydata
     readfiles <- lapply(mydata, read.csv)
     ## combine all the files into one file so that we can calculate the mean at once
     combine <- do.call(rbind,readfiles)
     ##calculate the mean without the NA values
     mean(combine[,pollutant], na.rm = TRUE)
}
```

```{r}
pollutantmean("specdata", "nitrate", 70:72)
```
```{r}
pollutantmean <- function(directory, pollutant, id = 1:332) {
  fileList <- list.files(path = directory, pattern = ".csv", full.names = TRUE)
  values <- numeric()
  
  for (i in id) {
    data <- read.csv(fileList[i])
    values <- c(values, data[[pollutant]])
  }
  mean(values, na.rm = TRUE)
}
```

```{r}
pollutantmean("specdata", "nitrate", 70:72)
```
```{r}
# install.packages("data.table")
library("data.table")

pollutantmean <- function(directory, pollutant, id = 1:332) {
  
  # Format number with fixed width and then append .csv to number
  fileNames <- paste0(directory, '/', formatC(id, width=3, flag="0"), ".csv" )
  
  # Reading in all files and making a large data.table
  lst <- lapply(fileNames, data.table::fread)
  dt <- rbindlist(lst)
  
  if (c(pollutant) %in% names(dt)){
    return(dt[, lapply(.SD, mean, na.rm = TRUE), .SDcols = pollutant][[1]])
  } 
}
```

```{r}
pollutantmean("specdata", "nitrate", 70:72)
```

Part 2
Write a function that reads a directory full of files and reports the number of completely observed cases in each data file. The function should return a data frame where the first column is the name of the file and the second column is the number of complete cases. A prototype of this function follows


```{r}
# Best method
complete <- function(directory, id = 1:332) {
     ## obtaining the required files by storing them into mydata variable
     mydata <- list.files(path =directory,pattern="*.csv", full.names=TRUE)[id]
     ## create an empty vector
     frows <- c()
     counter <- 1
     for(file_name in mydata) {
          ## storing each .csv file without the NA values into fineobject variable
          fineobject <- na.omit(read.csv(file_name))
          ## store the number of the fineobject rows in the empty f(ine)rows vector
          frows[counter] <- nrow(fineobject)
          counter <- counter + 1
     }
      ## creating and printing the f(ine)list
      flist <- data.frame("id" = id, "nobs" = frows)
      print(flist)
}

```

```{r}
complete("specdata", c(2, 4, 8, 10, 12))
complete("specdata", 30:25)
complete("specdata", 2)
```
```{r}
complete <- function(directory, id = 1:332) {
  filelist <- list.files(path = directory, pattern = ".csv", full.names = TRUE)
  print(paste("##", "", "id", "nobs", sep = " "))
  counter <- 0
  for (i in id) {
    counter <- counter + 1
    data = read.csv(filelist[i])
    print(paste("##", counter, i, sum(complete.cases(data)), sep=" "))
  }
}
```

```{r}
complete("specdata", 30:25)
```
```{r}
complete <- function(directory,  id = 1:332) {
  
  # Format number with fixed width and then append .csv to number
  fileNames <- paste0(directory, '/', formatC(id, width=3, flag="0"), ".csv" )
  
  # Reading in all files and making a large data.table
  lst <- lapply(fileNames, data.table::fread)
  dt <- rbindlist(lst)
  
  return(dt[complete.cases(dt), .(nobs = .N), by = ID])
  
}
```

```{r}
complete("specdata", 30:25)
```
```{r}
directory <-"specdata"
id <- 30:25
fileNames <- paste0(directory, '/', formatC(id, width=3, flag="0"), ".csv" )
# Reading in all files and making a large data.table
lst <- lapply(fileNames, data.table::fread)
dt <- rbindlist(lst)
dt
```
```{r}
#Return a logical vector indicating which cases are complete, i.e., have no missing values.
#complete.cases(dt)
```

Part 3
Write a function that takes a directory of data files and a threshold for complete cases and calculates the correlation between sulfate and nitrate for monitor locations where the number of completely observed cases (on all variables) is greater than the threshold. The function should return a vector of correlations for the monitors that meet the threshold requirement. If no monitors meet the threshold requirement, then the function should return a numeric vector of length 0. A prototype of this function follows

```{r}
corr <- function(directory, threshold = 0) {
  
  # Reading in all files and making a large data.table
  lst <- lapply(file.path(directory, list.files(path = directory, pattern="*.csv")), data.table::fread)
  dt <- rbindlist(lst)
  
  # Only keep completely observed cases
  dt <- dt[complete.cases(dt),]
  
  # Apply threshold
  dt <- dt[, .(nobs = .N, corr = cor(x = sulfate, y = nitrate)), by = ID][nobs > threshold]
  return(dt[, corr])
}
```


```{r}
cr <- corr("specdata", 150)
head(cr)
```


```{r}
```

https://zenagiwa.wordpress.com/2016/06/08/r-programming-assignment-1/

```{r}
pollutantmean<-function(directory,pollutant,id=1:332){
  #create a list of files
  filesD<-list.files(directory,full.names = TRUE)
  #create an empty data frame
  dat <- data.frame()
  
  #loop through the list of files until id is found
  for(i in id){
    #read in the file
    temp<- read.csv(filesD[i],header=TRUE)
    #add files to the main data frame
    dat<-rbind(dat,temp)
  }
  #find the mean of the pollutant, make sure you remove NA values
  return(mean(dat[,pollutant],na.rm = TRUE))
  
}

pollutantmean("specdata", "nitrate", 70:72)
```


```{r}
complete <- function(directory,id=1:332){

#create a list of files
  filesD<-list.files(directory,full.names = TRUE)
  #create an empty data frame
  dat <- data.frame()
  
  for(i in id){
  #read in the file
    temp<- read.csv(filesD[i],header=TRUE)
    #delete rows that do not have complete cases
    temp<-na.omit(temp)
    
    #count all of the rows with complete cases
    nobs<-nrow(temp)
    
    #enumerate the complete cases by index
    dat<-rbind(dat,data.frame(i,nobs))
   
  }
    return(dat)
}

complete("specdata", 30:25)
```


```{r}
corr<-function(directory,threshold=0){
#create list of file names
  filesD<-list.files(directory,full.names = TRUE)
  
  #create empty vector
  dat <- vector(mode = "numeric", length = 0)
  
  for(i in 1:length(filesD)){
  #read in file
    temp<- read.csv(filesD[i],header=TRUE)
    #delete NAs
    temp<-temp[complete.cases(temp),]
    #count the number of observations
    csum<-nrow(temp)
    #if the number of rows is greater than the threshold
    if(csum>threshold){
   #for that file you find the correlation between nitrate and sulfate
   #combine each correlation for each file in vector format using the concatenate function 
   #since this is not a data frame we cannot use rbind or cbind
      dat<-c(dat,cor(temp$nitrate,temp$sulfate))
    }
    
  }

  return(dat)
}
```


```{r}
cr <- corr("specdata", 400)
head(cr)
```

```{r}
cr <- corr("specdata", 2000)                
n <- length(cr)                
cr <- corr("specdata", 1000)                
cr <- sort(cr)
print(c(n, round(cr, 4)))
```

