---
title: "Untitled"
output: html_document
---
1. Have total emissions from PM2.5 decreased in the United States from 1999 to 2008? Using the base plotting system, make a plot showing the total PM2.5 emission from all sources for each of the years 1999, 2002, 2005, and 2008.
```{r}
NEI_path <- "/media/ad/01D6B57CFBE4DB20/1.Linux/Data/JHU data/exdata_data_NEI_data/summarySCC_PM25.rds"
SCC_path <- "/media/ad/01D6B57CFBE4DB20/1.Linux/Data/JHU data/exdata_data_NEI_data/Source_Classification_Code.rds"
```


```{r}
## This first line will likely take a few seconds. Be patient!
NEI <- readRDS(NEI_path)
SCC <- readRDS(SCC_path)
```


```{r}
dim(NEI)
dim(SCC)
```


```{r}
head(NEI)
```
- fips: A five-digit number (represented as a string) indicating the U.S. county
- SCC: The name of the source as indicated by a digit string (see source code classification table)
- Pollutant: A string indicating the pollutant
- Emissions: Amount of PM2.5 emitted, in tons
- type: The type of source (point, non-point, on-road, or non-road)
- year: The year of emissions recorded

```{r}
str(NEI)
```

```{r}
head(SCC)
```
```{r}
str(SCC)
```


```{r}
library(tidyverse)
```

```{r}
summary(NEI)
```
```{r}
NEI
NEI$year <- as.factor(NEI$year)
```

```{r}
class(NEI)
```

```{r}
total_emissions_by_year <- NEI %>% group_by(year) %>% summarise(sum_all = sum(Emissions))
total_emissions_by_year
```
```{r}
class(total_emissions_by_year)
```

```{r}
total_emissions_by_year %>% 
  ggplot(aes(x=year,y=sum_all))+
  geom_bar(stat = "identity")
  #geom_line()
```

```{r}
with(total_emissions_by_year,barplot(sum_all,names = year,
         xlab = "Years", ylab = "Emissions",
         main = "Emissions over the Years"
         ))
```



2. Have total emissions from PM2.5 decreased in the Baltimore City, Maryland fips == "24510" from 1999 to 2008? Use the base plotting system to make a plot answering this question.

```{r}
NEI
```


```{r}
Baltimore_PM <-NEI %>% filter(fips == 24510) %>% 
                group_by(year) %>% 
                summarise(sum_all = sum(Emissions))
Baltimore_PM
```


```{r}
with(Baltimore_PM,barplot(sum_all,names = year,
         xlab = "Years", ylab = "Emissions",
         main = "Emissions over the Years in Baltimore City"
         ))
```

3. Of the four types of sources indicated by the type (point, nonpoint, onroad, nonroad) variable, which of these four sources have seen decreases in emissions from 1999–2008 for Baltimore City? Which have seen increases in emissions from 1999–2008? Use the ggplot2 plotting system to make a plot answer this question.
```{r}
Baltimore_PM <-NEI %>% filter(fips == 24510)
Baltimore_PM
```
```{r}
names(Baltimore_PM)
```

```{r}
Baltimore_PM %>% 
  ggplot(aes(factor(year),Emissions,fill=type))+
  geom_bar(stat="identity") +
  facet_grid(.~type)+
  labs(title=expression("PM Emissions, Baltimore City 1999-2008 by Source Type"))
```

4. Across the United States, how have emissions from coal combustion-related sources changed from 1999–2008?
```{r}
SCC
```

```{r}
levels(SCC$SCC.Level.One)
```

```{r}
levels(SCC$SCC.Level.Two)
```

```{r}
SCC[["SCC.Level.One"]]
```

```{r}
combustionRelated <- grepl("comb", SCC[["SCC.Level.One"]], ignore.case=TRUE)
coalRelated <- grepl("coal", SCC[["SCC.Level.Four"]], ignore.case=TRUE) 
```


```{r}
combustionSCC <- SCC %>% filter(combustionRelated & coalRelated)
combustionSCC
```
```{r}
combustionNEI <- NEI %>% filter(SCC %in% combustionSCC$SCC )
combustionNEI
```
```{r}
ggplot(combustionNEI,aes(x = factor(year),y = Emissions/10^5)) +
  geom_bar(stat="identity", fill ="#FF9999", width=0.75) +
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (10^5 Tons)")) + 
  labs(title=expression("PM"[2.5]*" Coal Combustion Source Emissions Across US from 1999-2008"))

```

5. How have emissions from motor vehicle sources changed from 1999–2008 in Baltimore City?

```{r}
vehicles <- grepl("vehicle", SCC[["SCC.Level.Two"]], ignore.case=TRUE)
vehiclesSCC <- SCC %>% filter(vehicles)
vehiclesNEI <- NEI %>% filter(SCC %in% vehiclesSCC$SCC )
```

```{r}
baltimoreVehiclesNEI <- vehiclesNEI%>% filter(fips == 24510) 
```


```{r}
ggplot(baltimoreVehiclesNEI,aes(factor(year),Emissions)) +
  geom_bar(stat="identity", fill ="#FF9999" ,width=0.75) +
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (10^5 Tons)")) + 
  labs(title=expression("PM"[2.5]*" Motor Vehicle Source Emissions in Baltimore from 1999-2008"))
```

6.Compare emissions from motor vehicle sources in Baltimore City with emissions from motor vehicle sources in Los Angeles County, California (\color{red}{\verb|fips == "06037"|}fips == "06037"). Which city has seen greater changes over time in motor vehicle emissions?


```{r}
vehicles <- grepl("vehicle", SCC[["SCC.Level.Two"]], ignore.case=TRUE)
vehiclesSCC <- SCC %>% filter(vehicles)
vehiclesNEI <- NEI %>% filter(SCC %in% vehiclesSCC$SCC )
baltimoreVehiclesNEI <- vehiclesNEI%>% filter(fips == "24510") 
losangelessVehiclesNEI <- vehiclesNEI%>% filter(fips == "06037")
```
```{r}
baltimoreVehiclesNEI<-baltimoreVehiclesNEI %>% mutate(city="Baltimore City")
losangelessVehiclesNEI<-losangelessVehiclesNEI %>% mutate(city="Los Angeles")
baltimoreVehiclesNEI
losangelessVehiclesNEI
```

```{r}
# Combine data.tables into one data.table
bothNEI <- rbind(baltimoreVehiclesNEI,losangelessVehiclesNEI)
bothNEI
```
```{r}
ggplot(bothNEI, aes(x=factor(year), y=Emissions, fill=city)) +
  geom_bar(aes(fill=year),stat="identity") +
  facet_grid(scales="free", space="free", .~city) +
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (Kilo-Tons)")) + 
  labs(title=expression("PM"[2.5]*" Motor Vehicle Source Emissions in Baltimore & LA, 1999-2008"))
```


```{r}
p <- ggplot(baltimoreVehiclesNEI,aes(factor(year),Emissions)) +
  geom_bar(stat="identity", fill ="#FF9999" ,width=0.75) +
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (10^5 Tons)")) + 
  labs(title=expression("PM"[2.5]*" Motor Vehicle Source Emissions in Baltimore from 1999-2008"))

q <- ggplot(losangelessVehiclesNEI,aes(factor(year),Emissions)) +
  geom_bar(stat="identity", fill ="#FF9999" ,width=0.75) +
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (10^5 Tons)")) + 
  labs(title=expression("PM"[2.5]*" Motor Vehicle Source Emissions in LA from 1999-2008"))
```


```{r}
library(ggpubr)
ggarrange(p,q,ncol = 2)
```

```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

