---
title: "Untitled"
output: html_document
---
1. Have total emissions from PM2.5 decreased in the United States from 1999 to 2008? Using the base plotting system, make a plot showing the total PM2.5 emission from all sources for each of the years 1999, 2002, 2005, and 2008.
```{r}
NEI_path <- "/media/ad/01D6B57CFBE4DB20/1.Linux/Data/JHU data/exdata_data_NEI_data/summarySCC_PM25.rds"
SCC_path <- "/media/ad/01D6B57CFBE4DB20/1.Linux/Data/JHU data/exdata_data_NEI_data/Source_Classification_Code.rds"
```


```{r}
## This first line will likely take a few seconds. Be patient!
NEI <- readRDS(NEI_path)
SCC <- readRDS(SCC_path)
```


```{r}
dim(NEI)
dim(SCC)
```


```{r}
head(NEI)
```
- fips: A five-digit number (represented as a string) indicating the U.S. county
- SCC: The name of the source as indicated by a digit string (see source code classification table)
- Pollutant: A string indicating the pollutant
- Emissions: Amount of PM2.5 emitted, in tons
- type: The type of source (point, non-point, on-road, or non-road)
- year: The year of emissions recorded

```{r}
str(NEI)
```

```{r}
head(SCC)
```
```{r}
str(SCC)
```


```{r}
library(tidyverse)
```

```{r}
summary(NEI)
```
```{r}
NEI
NEI$year <- as.factor(NEI$year)
```

```{r}
class(NEI)
```

```{r}
total_emissions_by_year <- NEI %>% group_by(year) %>% summarise(sum_all = sum(Emissions))
total_emissions_by_year
```
```{r}
class(total_emissions_by_year)
```

```{r}
total_emissions_by_year %>% 
  ggplot(aes(x=year,y=sum_all))+
  geom_bar(stat = "identity")
  #geom_line()
```

```{r}
with(total_emissions_by_year,barplot(sum_all,names = year,
         xlab = "Years", ylab = "Emissions",
         main = "Emissions over the Years"
         ))
```





```{r}
```


```{r}
```


```{r}
```


```{r}
```

```{r}
```


```{r}
```

