---
title: "EDA"
output: html_document
---
```{r}
library(tidyverse)
```

```{r}
library(data.table)
path <- "/media/ad/01D6B57CFBE4DB20/1.Linux/Data/household_power_consumption.txt"
data <- fread(path)
dim(data) # 2075259 9
head(data)
```
Description: Measurements of electric power consumption in one household with a one-minute sampling rate over a period of almost 4 years. Different electrical quantities and some sub-metering values are available.

Date: Date in format dd/mm/yyyy
Time: time in format hh:mm:ss
Global_active_power: household global minute-averaged active power (in kilowatt)
Global_reactive_power: household global minute-averaged reactive power (in kilowatt)
Voltage: minute-averaged voltage (in volt)
Global_intensity: household global minute-averaged current intensity (in ampere)
Sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but gas powered).
Sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light.
Sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an electric water-heater and an air-conditioner.
```{r}
str(data)
```

# Check missing value   
```{r}
sum(is.na(data))
```
```{r}
null_value <- sapply(data, function(x) sum(is.na(x)))
class(null_value)
null_value_df <- as.data.frame(null_value) %>% arrange(desc(null_value)) %>% filter(null_value > 0)
# Name the unnamed first column
null_value_df <- cbind(Features= rownames(null_value_df), null_value_df)
rownames(null_value_df) <- NULL
# Add percentage column
total_rows <- dim(data)[1]
null_value_df <- null_value_df %>% mutate(percentage=null_value/total_rows*100)
null_value_df
```

# Convert date and time data
```{r}
library(hms)
data$Date <- as.Date(data$Date)
data$Time <- as_hms(data$Time)
head(data)
```
```{r}
data <- data %>% mutate_if(is.character,as.numeric)
```

```{r}
head(data)
```
```{r}
library(corrplot)
M <-cor(data %>% select_if(is.numeric))
M
```
```{r}
corrplot(M, type="upper", order="original")
```

```{r}
library(corrplot)
source("http://www.sthda.com/upload/rquery_cormat.r")
rquery.cormat(data %>% select_if(is.numeric))
```
```{r}
rquery.cormat(data %>% select_if(is.numeric), type="full")
```
```{r}
rquery.cormat(data %>% select_if(is.numeric), graphType="heatmap")
```

```{r}
library(DataExplorer)
introduce(data)
```


```{r}
plot_intro(data)
```


```{r}
## View missing value distribution for airquality data
plot_missing(data)
```

```{r}
## View histogram of all continuous variables
plot_histogram(data)
```


```{r}
## View estimated density distribution of all continuous variables
plot_density(data)
```


```{r}
plot_correlation(data %>% select_if(is.numeric))
```


```{r}
## View bivariate continuous distribution based on `cut`
plot_boxplot(data,by="Voltage")
```


```{r}
## Scatterplot `price` with all other continuous features
plot_scatterplot(split_columns(data)$continuous, by = "Voltage", sampled_rows = 1000L)
```
# Datatable style
```{r}
library(data.table)
path <- "/media/ad/01D6B57CFBE4DB20/1.Linux/Data/household_power_consumption.txt"
#Reads in data from file then subsets data for specified dates
powerDT <- data.table::fread(path,
                             , na.strings="?"
                             )
```

```{r}
dim(powerDT)
```

```{r}
# Prevents histogram from printing in scientific notation
powerDT[, Global_active_power := lapply(.SD, as.numeric), .SDcols = c("Global_active_power")]

# Change Date Column to Date Type
powerDT[, Date := lapply(.SD, as.Date, "%d/%m/%Y"), .SDcols = c("Date")]

# Filter Dates for 2007-02-01 and 2007-02-02
powerDT <- powerDT[(Date >= "2007-02-01") & (Date <= "2007-02-02")]
png("plot1.png", width=480, height=480)
hist(powerDT[, Global_active_power], main="Global Active Power", 
     xlab="Global Active Power (kilowatts)", ylab="Frequency", col="Red")

```



```{r}
png("plot2.png", width=480, height=480)
# Prevents Scientific Notation
powerDT[, Global_active_power := lapply(.SD, as.numeric), .SDcols = c("Global_active_power")]

# Making a POSIXct date capable of being filtered and graphed by time of day
powerDT[, dateTime := as.POSIXct(paste(Date, Time), format = "%d/%m/%Y %H:%M:%S")]

# Filter Dates for 2007-02-01 and 2007-02-02
powerDT <- powerDT[(dateTime >= "2007-02-01") & (dateTime < "2007-02-03")]
## Plot 2
plot(x = powerDT[, dateTime]
     , y = powerDT[, Global_active_power]
     , type="l", xlab="", ylab="Global Active Power (kilowatts)")

#dev.off()
```


```{r}
png("plot3.png", width=480, height=480)

# Plot 3
plot(powerDT[, dateTime], powerDT[, Sub_metering_1], type="l", xlab="", ylab="Energy sub metering")
lines(powerDT[, dateTime], powerDT[, Sub_metering_2],col="red")
lines(powerDT[, dateTime], powerDT[, Sub_metering_3],col="blue")
legend("topright"
       , col=c("black","red","blue")
       , c("Sub_metering_1  ","Sub_metering_2  ", "Sub_metering_3  ")
       ,lty=c(1,1), lwd=c(1,1))
```


```{r}
png("plot4.png", width=480, height=480)

par(mfrow=c(2,2))

# Plot 1
plot(powerDT[, dateTime], powerDT[, Global_active_power], type="l", xlab="", ylab="Global Active Power")

# Plot 2
plot(powerDT[, dateTime],powerDT[, Voltage], type="l", xlab="datetime", ylab="Voltage")

# Plot 3
plot(powerDT[, dateTime], powerDT[, Sub_metering_1], type="l", xlab="", ylab="Energy sub metering")
lines(powerDT[, dateTime], powerDT[, Sub_metering_2], col="red")
lines(powerDT[, dateTime], powerDT[, Sub_metering_3],col="blue")
legend("topright", col=c("black","red","blue")
       , c("Sub_metering_1  ","Sub_metering_2  ", "Sub_metering_3  ")
       , lty=c(1,1)
       , bty="n"
       , cex=.5) 

# Plot 4
plot(powerDT[, dateTime], powerDT[,Global_reactive_power], type="l", xlab="datetime", ylab="Global_reactive_power")

dev.off()
```


```{r}
```


```{r}
```

