---
title: "Analysis of the Population Health effect and Economic consequences of US Storms"
author: "Nguyen Ngoc Duy"
date: "30/12/2020"
output: html_document
---
```{r}
getwd()
setwd("/home/ad/Data_science/R_studio/Git/datasciencecoursera/5. Reproducible_research")
```
## 1. Goal of this assignment:

The basic goal of this assignment is to explore the NOAA Storm Database and answer some basic questions about severe weather events. The data analysis  address the following questions:

- Across the United States, which types of events (as indicated in the \color{red}{\verb|EVTYPE|}EVTYPE variable) are most harmful with respect to population health?
- Across the United States, which types of events have the greatest economic consequences?

## 2. Data Processing
### 2.1 Load Data

```{r}
library(data.table)
library(tidyverse)
path <- "/media/ad/01D6B57CFBE4DB20/1.Linux/Data/JHU data/repdata_data_StormData.csv"
data <- fread(path)
head(data)
```
```{r}
# Convert EVTYPE to factor
data[,EVTYPE := lapply(.SD,as.factor), .SDcols= c("EVTYPE")]
```

### 2.2 Calcuating Total Fatalities and Injuries

```{r}
totalInjuries <- data[,.(FATALITIES = sum(FATALITIES), INJURIES = sum(INJURIES), totals = sum(FATALITIES) + sum(INJURIES)),by="EVTYPE"][order(-totals)]
totalInjuries <- totalInjuries[,head(.SD,10)]
totalInjuries
```

### 2.3 Calcuating Total Property and Crop Damage

```{r}
totaldamage <- data[,.(propCost = sum(PROPDMG), cropCost = sum(CROPDMG), Total_Cost = sum(PROPDMG) + sum(CROPDMG)),by="EVTYPE"][order(-Total_Cost)]
totaldamage <- totaldamage[,head(.SD,10)]
totaldamage
```

## 3. Results
### 3.1 Events that are Most Harmful to Population Health

Melting data.table so that it is easier to put in bar graph format
```{r}
totalInjuries_melt <- melt(totalInjuries, id.vars="EVTYPE", variable.name = "Health_harmful")
head(totalInjuries_melt,10)
```

```{r}
totalInjuries_melt %>% 
  ggplot(aes(x=reorder(EVTYPE,-value),y=value)) +
  geom_bar(stat="identity",aes(fill=Health_harmful),position="dodge") +
  labs(x="Event type", y=expression("number of Fatalities & Injuries")) + 
  labs(title=expression("Top 10 events causing Harmful to population health"))+
  theme(axis.text.x = element_text(angle=45, hjust=1))
```
Fig: Tornado is the most harmful to population health

### 3.2. Events that have the Greatest Economic Consequences

Melting data.table so that it is easier to put in bar graph format
```{r}
totaldamage_melt <- melt(totaldamage, id.vars="EVTYPE", variable.name = "economic_consquences")
head(totaldamage_melt,10)
```

```{r}
totaldamage_melt %>% 
  ggplot(aes(x=reorder(EVTYPE,-value),y=value)) +
  geom_bar(stat="identity",aes(fill=economic_consquences),position="dodge") +
  labs(x="Event type", y=expression("Property & Crop damage")) + 
  labs(title=expression("Top 10 events causing Economic consequences")) +
  theme(axis.text.x = element_text(angle=45, hjust=1))
```
Fig: Tornado is the most economic damage

