---
title: "regression model project"
output: html_document
---

```{r}
library(tidyverse)
data("mtcars")
mtcars
```
Motor Trend Car Road Tests

Description

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

A data frame with 32 observations on 11 (numeric) variables.

[, 1]	mpg	Miles/(US) gallon
[, 2]	cyl	Number of cylinders
[, 3]	disp	Displacement (cu.in.)
[, 4]	hp	Gross horsepower
[, 5]	drat	Rear axle ratio
[, 6]	wt	Weight (1000 lbs)
[, 7]	qsec	1/4 mile time
[, 8]	vs	Engine (0 = V-shaped, 1 = straight)
[, 9]	am	Transmission (0 = automatic, 1 = manual)
[,10]	gear	Number of forward gears
[,11]	carb	Number of carburetors

## Data exploration

```{r}
require(graphics)
pairs(mtcars, main = "mtcars data", gap = 1/4)
```

```{r}
coplot(mpg ~ disp | as.factor(cyl), data = mtcars,
       panel = panel.smooth, rows = 1)
```

```{r}
## possibly more meaningful, e.g., for summary() or bivariate plots:
mtcars2 <- within(mtcars, {
   vs <- factor(vs, labels = c("V", "S"))
   am <- factor(am, labels = c("automatic", "manual"))
   cyl  <- ordered(cyl)
   gear <- ordered(gear)
   carb <- ordered(carb)
})
summary(mtcars2)
```


```{r}
head(mtcars2)
```

## “Is an automatic or manual transmission better for MPG” 

```{r}
mtcars2 %>% 
  ggplot(aes(am,mpg,fill=am))+
  geom_boxplot()
```

```{r}
mpg_auto <- mtcars2$mpg[mtcars2$am == "automatic"]
mpg_manual <- mtcars2$mpg[mtcars2$am == "manual"]
```

Check assumtion: 
Assumtion : Are the data from each of the 2 groups follow a normal distribution?

```{r}
library(ggpubr)
ggqqplot(mpg_auto)
ggqqplot(mpg_manual)
```


```{r}
shapiro.test(mpg_auto)
shapiro.test(mpg_manual)
```
p value > 0.05 so we cannot reject hypothesis that all data is normal distribution

Assumption Do the two populations have the same variances?
```{r}
res.ftest <- var.test(mpg_auto,mpg_manual)
res.ftest
```
The p-value of F-test is greater than the significance level alpha = 0.05. In conclusion, there is no significant difference between the variances of the two sets of data. Therefore, we can use the classic t-test witch assume equality of the two variances.

```{r}
t.test(mpg_auto, mpg_manual, alternative = "less", paired = FALSE, var.equal = TRUE, conf.level = 0.95)
```
As the p-value  is lower than 0.05, then, we reject the null hypothesis. it means that mpg automatic less than mpg manual

## "Quantify the MPG difference between automatic and manual transmissions"  

```{r}
simple_model <- lm(mpg ~ am, data = mtcars)
summary(simple_model)
```
The R2 value is 0.36 thus telling us this model only explains us 36% of the variance. As a result, we need to build a multivariate linear regression.

```{r}
complex_model <- lm(mpg ~.,data=mtcars)
anova(simple_model,complex_model)
```


```{r}
summary(complex_model)
```


```{r}
```


```{r}
```

