---
title: "Regression_model_learn"
output: html_document
---
# Simple Linear Regression
the data for this example can be found here
the data contains the records 20 games for Baltimore Ravens, a professional American Football team
there are 4 columns
ravenWinNum = 1 for Raven win, 0 for Raven loss
ravenWin = W for Raven win, L for Raven loss
ravenScore = score of the Raven team during the match
opponentScore = score of the Raven team during the match
```{r}
# load the data
load("ravensData.rda")
head(ravensData)
```


```{r}
# perform linear regression
summary(lm(ravenWinNum ~ ravenScore, data = ravensData))
```
Lower R2, poor fit to data

# Logistic Regression

```{r}
# run logistic regression on data
logRegRavens <- glm(ravenWinNum ~ ravenScore, data = ravensData,family="binomial")
# print summary
summary(logRegRavens)
```


```{r}
# take e^coefs to find the log ratios
exp(logRegRavens$coeff)
```


```{r}
# take e^log confidence interval to find the confidence intervals
exp(confint(logRegRavens))
```
# General Linear Models - Poisson Models

- Poisson distribution is a useful model for counts and rates
rate = count per unit of time
linear regression with transformation is an alternative
- count data examples
calls to a call center
number of flu cases in an area
number of cars that cross a bridge
- rate data examples
percent of children passing a test
percent of hits to a website from a country
radioactive decay
- Poisson model examples
modeling web traffic hits incidence rates
approximating binomial probabilities with small p and large n
analyzing contingency table data (tabulated counts for categorical variables)

```{r}
# laod data
load("gaData.rda")
head(gaData)
```


```{r}
# convert the dates to proper formats
gaData$julian <- julian(gaData$date)
head(gaData)
```


```{r}
# plot visits vs dates
plot(gaData$julian,gaData$visits,pch=19,col="darkgrey",xlab="Julian",ylab="Visits")
```

```{r}
# construct Poisson regression model
glm1 <- glm(gaData$visits ~ gaData$julian,family="poisson")
summary(glm1)
```


```{r}
# perform linear regression
lm1 <- lm(gaData$visits ~ gaData$julian)
summary(lm1)
```


```{r}
# plot visits vs dates
plot(gaData$julian,gaData$visits,pch=19,col="darkgrey",xlab="Julian",ylab="Visits")
# plot linear regression line in red
abline(lm1,col="red",lwd=3)
# plot Poisson regression line in
lines(gaData$julian,glm1$fitted,col="blue",lwd=3)
```
Note: the Poisson fit is non-linear since it is linear only on the log of the mean scale

```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

