---
title: "regression model project"
Name: Nguyen Ngoc Duy
Date: Jan, 04, 2021
output:
  pdf_document: default
  html_document: default
---
## Executive Summary

In this report, we will examine the mtcars data set and explore how miles per gallon (MPG) is affected by different variables. In particularly, we will answer the following two questions: (1) Is an automatic or manual transmission better for MPG, and (2) Quantify the MPG difference between automatic and manual transmissions.

From our analysis we can show that manual transmission has an MPG 2.8 greater than an automatic transmission.


```{r}
library(tidyverse)
data("mtcars")
head(mtcars)
```
Motor Trend Car Road Tests

Description

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

A data frame with 32 observations on 11 (numeric) variables.

[, 1]	mpg	Miles/(US) gallon
[, 2]	cyl	Number of cylinders
[, 3]	disp	Displacement (cu.in.)
[, 4]	hp	Gross horsepower
[, 5]	drat	Rear axle ratio
[, 6]	wt	Weight (1000 lbs)
[, 7]	qsec	1/4 mile time
[, 8]	vs	Engine (0 = V-shaped, 1 = straight)
[, 9]	am	Transmission (0 = automatic, 1 = manual)
[,10]	gear	Number of forward gears
[,11]	carb	Number of carburetors

## EDA

```{r}
## possibly more meaningful, e.g., for summary() or bivariate plots:
mtcars2 <- within(mtcars, {
   vs <- factor(vs, labels = c("V", "S"))
   am <- factor(am, labels = c("automatic", "manual"))
   cyl  <- ordered(cyl)
   gear <- ordered(gear)
   carb <- ordered(carb)
})
summary(mtcars2)
```


```{r}
head(mtcars2)
```

## “Is an automatic or manual transmission better for MPG” 

```{r}
mtcars2 %>% 
  ggplot(aes(am,mpg,fill=am))+
  geom_boxplot()
```

```{r}
mpg_auto <- mtcars2$mpg[mtcars2$am == "automatic"]
mpg_manual <- mtcars2$mpg[mtcars2$am == "manual"]
```

Check assumtion: 
Assumtion : Are the data from each of the 2 groups follow a normal distribution?

```{r}
library(ggpubr)
ggqqplot(mpg_auto)
ggqqplot(mpg_manual)
```


```{r}
shapiro.test(mpg_auto)
shapiro.test(mpg_manual)
```
p value > 0.05 so we cannot reject hypothesis that all data is normal distribution

Assumption Do the two populations have the same variances?
```{r}
res.ftest <- var.test(mpg_auto,mpg_manual)
res.ftest
```
The p-value of F-test is greater than the significance level alpha = 0.05. In conclusion, there is no significant difference between the variances of the two sets of data. Therefore, we can use the classic t-test witch assume equality of the two variances.

```{r}
t.test(mpg_auto, mpg_manual, alternative = "less", paired = FALSE, var.equal = TRUE, conf.level = 0.95)
```
As the p-value  is lower than 0.05, then, we reject the null hypothesis. it means that mpg automatic less than mpg manual

## "Quantify the MPG difference between automatic and manual transmissions"  

```{r}
simple_model <- lm(mpg ~ am, data = mtcars)
summary(simple_model)
```
The R2 value is 0.36 thus telling us this model only explains us 36% of the variance. As a result, we need to build a multivariate linear regression.

```{r}
complex_model <- lm(mpg ~.,data=mtcars)
anova(simple_model,complex_model)
```

p-value < 0.05 so we can claim the complex_model model is significantly better than our simple_model model.
```{r}
summary(complex_model)
```
The model explains 86.9% of the variance and as a result, Thus, we can say the difference between automatic and manual transmissions is 2.81 MPG.
## Appendix

- Check residuals
```{r}
par(mfrow = c(2,2))
plot(complex_model)
```
```{r}
require(graphics)
pairs(mtcars, main = "mtcars data", gap = 1/4)
```

```{r}
```

