---
title: "Job attrition analytyic"
author: "Nguyen Ngoc Duy"
date: "Jan 9, 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE,message = FALSE,warning = FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
```
## Some information

- Github link to shiniapp code, data file and presentation file:
https://github.com/duybluemind1988/datasciencecoursera/tree/main/9.%20Develop%20Data%20product/Job_attrition

- Job attrition instroduction:
Uncover the factors that lead to employee attrition and explore important questions such as ‘show me a breakdown of distance from home by job role and attrition’ or ‘compare average monthly income by education and attrition’. This is a fictional data set created by IBM data scientists.

- Link to Kaggle job attrition information:
https://www.kaggle.com/pavansubhasht/ibm-hr-analytics-attrition-dataset

```{r message = FALSE,warning = FALSE,include=FALSE}
library(data.table)
library(tidyverse)
library(rsample)   # for data splitting
library(h2o)
library(caret)
h2o.no_progress()
h2o.init()
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
path <- "WA_Fn-UseC_-HR-Employee-Attrition.csv"
data <- fread(path)
# Create training (80%) and test (20%) sets for the 
set.seed(430)
split = createDataPartition(data$Attrition, p =0.8, list = FALSE)
train = data[split, ]
test = data[-split, ]
# all character columns to factor:
train <- mutate_if(train, is.character, as.factor)
column_near_zero_var <-nearZeroVar(train)
train <- train[,-..column_near_zero_var]
test <- mutate_if(test, is.character, as.factor)
test <- test[,-..column_near_zero_var]
# convert training data to h2o object
train_h2o <- as.h2o(train)
test_h2o <- as.h2o(test)
```
## Plot categorical vs catagorical
Compare Attirition percentage between business travel catagorical
```{r}
Categorical_vs_categorical_plot <- function(data,group_col,fill_col){
data %>%
  group_by_(group_col, fill_col) %>%
  summarize(n = n()) %>% 
  mutate(pct = n/sum(n),lbl = scales::percent(pct))%>% 
  ggplot(aes_(x = group_col,y = ~pct,
           fill = fill_col)) +
  geom_bar(stat = "identity",
           position = "fill") +
  scale_y_continuous(breaks = seq(0, 1, .2),label =scales::percent) +
  geom_text(aes(label = lbl), 
            size = 3, 
            position = position_stack(vjust = 0.5)) +
  #scale_fill_brewer(palette = "Set2") +
  labs(y = "Percent",x = "Attrition",title = "Compare attrition accross category")+
  theme_minimal()  
  
}
Categorical_vs_categorical_plot(data,~Attrition,~BusinessTravel)
```

```{r}
# load the model
model_path <- "GBM_model_R_1610154635473_1"
h2o_model <- h2o.loadModel(model_path)
```

## Variable important
```{r}
h2o.varimp_plot(h2o_model)
```

## Shap explain model
```{r}
h2o.shap_summary_plot(h2o_model,test_h2o)
```
